The genomic impacts of drift and selection for hybrid performance in maize

### 2015-07-07 main.tex
figures modified, added to supp.

\usepackage{color}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geneticsT2}
\usepackage{times}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{amsmath}

@@

\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.90}
\renewcommand{\dbltopfraction}{0.95}
\renewcommand{\dblfloatpagefraction}{0.80}
\renewcommand{\sfdefault}{phv}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIGURE
\begin{figure*}[tb]   
  \begin{center}
  % \vspace{-0mm}
   \includegraphics[width=0.8\linewidth]{Fig4/fig4_combined}
 %  \renewcommand{\baselinestretch}{0.9}
 %  \vspace{-3mm}
   \caption{\rev{Heterozygosity} in each cycle across chromosome 4 of the BSSS (left) and  BSCB1 (right) plotted on the physical (top) and genetic (bottom) map. \rev{Each panel consists of five plots representing cycles 0,4,8,12, and 16 of the experiment.} \rev{Heterozygosity} is calculated on 15-marker sliding windows, with 5 marker steps between each calculation. Each data point is color-coded based on a linear transformation of recombination rate (red = low recombination rate). Shaded regions represent 2 cM windows found to have heterozygosity values significantly lower than expected by simulation at a given cycle. Light shading denotes significance at $P<0.0025$, whereas the darker shading represents significance at $P<0.001$. Comparing the physical and genetic maps reveals that the regions of fixation are extremely small genetically, but some contain much of the physical content of the chromosome.
} 
\vspace{-6mm}
    \label{fig:genphys}
  \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIGURE

>>>>

\usepackage{color}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geneticsT2}
\usepackage{times}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{capt-of}

@@

\newcommand\Image[3][]{%
  \tabular[b]{@{}c@{}}\includegraphics[#1]{#2}\\
    #3
  \endtabular}
\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.90}
\renewcommand{\dbltopfraction}{0.95}
\renewcommand{\dblfloatpagefraction}{0.80}
\renewcommand{\sfdefault}{phv}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIGURE
\begin{figure*}[tb]   
  \begin{center}
  % \vspace{-0mm}
   \includegraphics[width=0.8\linewidth]{Fig4/chrom4_combined}
 %  \renewcommand{\baselinestretch}{0.9}
 %  \vspace{-3mm}
   \caption{\rev{Heterozygosity} in each cycle across chromosome 4 of the BSSS (left) and  BSCB1 (right) plotted on the physical (top) and genetic (bottom) map. \rev{Each panel consists of five plots representing cycles 0,4,8,12, and 16 of the experiment. Heterozygosity} is calculated on 15-marker sliding windows, with 5 marker steps between each calculation. Each data point is color-coded based on a linear transformation of recombination rate (red = low recombination rate). Shaded regions represent 2 cM windows with heterozygosity values significantly lower than expected by simulation at a given cycle. \rev{Light and darker shading denotes significance at $P<0.0025$ and $P<0.001$, respectively. Plots for other chromosomes are shown in in Figure \ref{fig:others2}}. Comparing the physical and genetic maps reveals that the regions of fixation are extremely small genetically, but some contain much of the physical content of the chromosome.
} 
\vspace{-6mm}
    \label{fig:genphys}
  \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIGURE
